Human Pose Estimation for Video Game Control

### 2022-05-07 paper/paper.tex
Finished pose estimation section

\section{Methodology}
Our human computer interface will consist of three major steps: Pose Estimation, or feature 
location, Feature Tracking and classification of motions, and video game interfacing. Each one 
is detailed below. All code will be written in Python.

\subsection{Pose Estimation}
The first step of our human computer interface pipeline is the pose estimation step, in which 
we use openpose to locate certain key features of the user. What constitutes a key feature will 
be determined when the set of video game controls we must mimic is properly defined. Possible 
key features include the location of the user's wrists, elbows, or the angles of various limbs.

During this step we will also determine the computational cost of openpose and make decisions on 
how to proceed based on the results. If openpose is able to run with sufficiently low latency, we 
move on to feature tracking, but if openpose demonstrates a high latency, we will explore other 
methods of pose estimation, or methods of improving the performance of openpose using by decreasing 
framerates or image resolutions.

\subsection{Feature Tracking}
Obtaining the locations of various important features is only the first step towards identifying 
physically-meaningful actions of the user. In order for the user to be able to signal various 
commands within the video game, we must track the previously obtained features over time and 
classify the user's behavior into one of a few possible actions. For example, mimicing a car 
racing game, the set of possible actions could be \{No command, accelerate, decelerate, steer\}. 
Each of these commands or classifications will also have a value associated with it corresponding 
to its magnitude, which will also be obtained directly from feature locations. For example, a steering 
command mapped to the user rotating their torso would have a steering value associated with it 
derived from the angle through which the user has turned.

\subsection{Game Interface}
The third and final major step of our methodology is to turn the classifications obtained from 
the Feature Tracking step and feed them to a video game as user input. We will simply map each 
corresponding classification from step 2 to an "intermediate control" which is simply the 
joystick/keyboard/mouse input that would produce the same output from the game, and implement 
simple keyboard control with Python to feed that input to the video game.

@@

\section{Future Works}

>>>>

\section{Methodology}
Our human computer interface consists of three major steps: Pose Estimation, or feature 
location, Feature Tracking and classification of motions, and video game interfacing. In addition, 
we adopt a multi-phased approach to our human computer interface. Phase 1 consists of a robust and 
general human pose estimator and keypoint detector. The work in Phase 1 is task/game agnostic, as 
we implement identical versions of this phase for the car-racer game as well as the chrome 
dinosaur game. Phase 2 is a game-specific keypoint classifier, where the output from Phase 1 is 
classified into a number of computer commands in a way dependent on the physical motions being 
replicated in the game as well as the computer commands the game is traditionally played with.\\

The motivation behind such a two phase approach rather than building a classifier that directly 
maps input video streams to computer commands is to improve the versatility of our human-computer 
interaction system. A fully general Phase 1 implemented independent of the game in question allows 
the system to be more easily adapted to any particular set of computer commands. We demonstrate the 
versatility of this system through the implementation of our human-computer interface for two 
distinct video games that utilize identical Phase 1 code.

\subsection{Testing Pose Estimation Methods}
Before we develop phase 1 of our human-computer interface, we test a number of proposed solutions 
for human pose estimation to determine which ones are best-suited to our needs. The main criteria 
we require for our human pose estimator are:

\begin{itemize}
    \item Real time operation. The need for this criterion is obvious, as we require low latency 
        classification in order to mimic low-latency commmands for video games. Essentially, the user 
        should feel as if the delay between executing a physical command and the video game reflecting 
        such a command is instantaneous.
    \item The system should be minimally intrusive on the computer used to play the game. This 
        essentially means that we cannot use computing resources so significant that usability of 
        the computer itself is diminished. 
\end{itemize}

\subsubsection{Openpose Python API}
The openpose package offers a Python API for implementing inference over video feeds using one 
of the openpose models. We began testing the openpose Python API for our task, but found that 
installing the API resulted in dependency issues accross multiple team members' computers and 
decided to instead test the openpose pretrained models implemented independently of the openpose 
python API.

%https://learnopencv.com/deep-learning-based-human-pose-estimation-using-opencv-cpp-python/
\subsubsection{Openpose model implemented in OpenCV}
(citation) offers a method to perform inference on CPU/GPU using pretrained versions of the 
openpose hand/body pose estimators. For inference with the openpose pretrained model through 
OpenCV, we observed only 1-2 FPS on a 2.3 GHz Intel i9 CPU. We expect that running the same model 
with CUDA acceleration would result in true real-time performance, but as one of our design 
constraints for our system, we imposed that we cannot use significant GPU resources in order to 
maintain minimal intrusiveness onto the gaming machine.

\subsubsection{PoseNet and the Jetson Nano}
Due to the poor performance of the Openpose models, we began to look at different methods for 
real-time pose estimation. One option that was promising was to completely offload the task of 
human pose estimation to an edge-device to reduce the computational burden on the device used 
to play the games. Such an embedded device would ideally be compact yet powerful enough to run 
quantized versions of pose estimators in real time. We found the NVIDIA Jetson Nano to be an 
ideal candidate for such an embedded device.\\

With a 128-core NVIDIA GPU on a single-board computer footprint, the Jetson Nano is a popular 
choice for deep model inference on embedded computers. Perhaps more important than the hardware 
itself, however, is the specific Tensor RT optimized models available for use on the Jetson Nano. 
Through a number of optimization techniques such as model quantization, unuzed output elimination 
and horizontal layer fusion/layer aggregation, the Tensorflow with Tensor RT (TF-TRT) backend is 
able to greatly improve inference time on the Jetson Nano. TF-TRT is able to output optimized 
models from Open Neural Network Exchange Format (ONXX) and for popular tasks such as human pose 
estimation, ONXX model formats are readily available from NVIDIA Developers.

\subsection{Pose Estimation}
Using a variant of PoseNet built on a ResNet-18 backbone, we observe 15-17 Frames Per Second 
(FPS) on the Jetson Nano. The so called Pose-ResNet-18-body outputs 17 detected keypoints in 
image coordinate format. 15-17 FPS performance is smooth enough keypoint detection to allow us to 
play these simple games in real time.

\subsection{Feature Tracking and Classification}
\subsubsection{Feature Classification For Steering}
\subsubsection{Feature Classification For Jumping/Ducking}

\subsection{Game Interface}

@@

\section{Conclusion and Future Works}
